\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage{pmboxdraw}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{hyperref}
\usepackage{graphicx}

\usepackage{titlesec}
\title{The New Vegan}

\titleformat{\chapter}[display]
{\normalfont\bfseries}{}{0pt}{\Huge}

\begin{document}
\frontmatter
\maketitle
\section*{Preface}
There haven't been many highlights over the past few years, I guess a global pandemic will do that. However, while many turned to sourdough and paint by numbers, I was lucky to have many willing victims to try my new cooking creations. Be it possibly illicit dinner parties or even just quite creative nights by myself, it has been a joy and relief to escape the drudgery of the world outside of the kitchen. Over the years I have cooked many wonderful recipes for many wonderful people, but at times inspiration has been hard to come by. Without fail, however, Meera Sodha et al's blog `The New Vegan' has been a constant source of inspiration when it has been lacking. I hope that whoever reads this can share a little bit of Meera joy with themselves or whomever they find themselves feeding. \\ \\ 
%
Unfortunately, one day you must grow up and get a real job. With physics not really being that enjoyable (this might shock you), I think a career as a data scientist beacons. In an effort to learn how to web scrape (so I will one day be able to steal all your data), I gave myself the task of turning my favourite cooking blog into a cookbook. This pdf is the result of that project. It is a relatively complete collection of recipes as of April 2022, but it may be updated in the future (if I've not been sued by that point). As with all the best cookbooks, I have organised it by the month the recipe was published so that you can find some seasonal inspiration. I am sorry if there are any funky formatting issues - the point of this project, beyond having a really good selection of vegan recipes, was to learn how to automate such a task rather than copy each one by hand. If you would like to play around with the code then do get in touch. \\ \\
%
I should stress that none of these recipes are my own. They all come from the Guardian's blog called \href{https://www.theguardian.com/food/series/the-new-vegan}{`The New Vegan'} \\ \\
%
DD 

\tableofcontents

\mainmatter